---
title: "011-Python-AWS-pipeline"
author: "JJayes"
date: "17/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(reticulate)
library(here)
```

```{python}
# !pip install boto3[crt]
import boto3
```

First I have to configure the AWS client with my credeitnials. To do this I need to install the [AWS shell](https://github.com/awslabs/aws-shell)?


```{python}
# !pip install aws-shell

# initialize the textract client
client = boto3.client('textract', region_name = 'us-east-2')
```

 
# analyze_document
This command is useful if you have tabular data.

# detect_document_text
 This command takes your input image and identifies all the blocks of text - gives you all the lines of text and pages.

You can provide your image as a pointer to an s3 object, or use a bytes encoded document that you have stored locally. That's the only parameter we need to set.

First I need to convert my pdf to jpeg. I'm gonna use imagemagick in R here.

```{r}
library(magick)

# pdf <- image_read_pdf(here("data", "test-patents", "SE2555_C1.pdf"))
# 
# jpeg <- image_convert(pdf, format = "jpeg")
# 
# page_1 <- jpeg[1]
# page_2 <- jpeg[2]
# 
# page_1 %>% image_write(here("data", "test-patents", "SE2555_C1_1.jpeg"))
# page_2 %>% image_write(here("data", "test-patents", "SE2555_C1_2.jpeg"))
```


```{python}
# also need to find equivalent of here package
# !pip install pyprojroot
from pyprojroot import here

here()
```


```{python}
# use image strored in s3
response = client.detect_document_text(Document = {
  'S3Object': {
    'Bucket': 'swedish-patent-data',
    'Name': 'test-patents/SE2555_C1_1.jpeg'
  }
  
})

print(response)
```

```{python}
response.keys()

response["DocumentMetadata"]

response['DetectDocumentTextModelVersion']

response["ResponseMetadata"]
```

We care about

```{python}
response["Blocks"]

blocks = response["Blocks"]
```

Each object in the list will be a section defining a block of output. So 

```{python}
len(blocks)
```

Each block provides a block type and geometry information 

```{python}
blocks[0]
```

What are the items?

```{python}
from collections import Counter

block_counts = Counter(x["BlockType"] for x in blocks)

block_counts
```

So we see we have 554 words, 85 lines and one page.

```{python}
blocks[3]
```

## Get all the lines from the image

```{python}
all_lines = [l for l in blocks if l["BlockType"] == "LINE"]

len(all_lines)
```


```{python}
for i in all_lines:
  print(i["Text"])
  
```

## Making use of other textract output to combine lines in a logical way

Keep the columns together

```{r}

```


# Trying to get a table out
# analyze_document

```{r}
library(magick)

pdf <- image_read_pdf(here("data", "ransom", "Egentliga Finland_11_16.pdf"))

jpeg <- image_convert(pdf, format = "jpeg")

page_1 <- jpeg[1]
page_2 <- jpeg[2]

page_1 %>% image_write(here("data", "ransom", "Egentliga Finland_11_16_1.jpeg"))
page_2 %>% image_write(here("data", "ransom", "Egentliga Finland_11_16_2.jpeg"))
```

Function to get images

```{r}
image_pre_process <- function(path) {
  message("Reading in image")
  pdf <- image_read_pdf(path)
  
  message("Converting image")
  jpeg <- image_convert(pdf, format = "jpeg")
  
  message("Getting number of pages")
  n_pages <- magick::image_info(jpeg) %>% nrow()
  
  for (i in 1:n_pages){
    message(paste0("Transforming and saving image ", i))
      page <- jpeg[i]
      
      page <- page %>% 
        image_deskew(threshold = 80) %>% 
        image_quantize(max = 255, colorspace = "gray", dither = T)
      
      page %>% image_write(glue::glue(here("data", "ransom", "Egentliga Finland_11_16_{i}_255_gray_dither.jpeg")))
  
  }
    
}


path <- here("data", "ransom", "Egentliga Finland_11_16.pdf")

image_pre_process(path = path)
```

### Pre-processing image

```{r}
image <- image_read(here("data", "riksvakanslistan", "gold_standard_1.JPG"))

image %>% 
  image_deskew() %>% 
  image_despeckle() %>% 
  image_quantize(max = 255, colorspace = "gray", dither = T) %>% image_write(here("data", "riksvakanslistan", "gold_standard_1_processed.JPG"))

```

```{r}
files <- list.files(here("data", "ransom")) %>% 
  as_tibble() %>% 
  filter(str_detect(value, "\\.jpeg"))

files %>% write.csv(here("data", "ransom", "images_to_upload.csv"))
```


```{python}
import pandas as pd

files = pd.read_csv(here("data/ransom/images_to_upload.csv"))

client_s3 = boto3.client('s3', region_name='us-west-2')

client_s3.upload_file(
  Filename=here("data/ransom/Egentliga Finland_11_16_1_255_gray_dither.jpeg"), 
  Bucket="swedish-patent-data")
```


```{python}


client_s3.upload_file('images/image_0.jpg', 'mybucket', 'image_0.jpg')

for i in files:
  print(i)
  
  
  
  client_s3.upload_file(print(here("data/ransom/", i), 'swedish-patent-data', i)
  



```


```{python}
response = client.analyze_document(
  Document = {
  'S3Object': {
    'Bucket': 'swedish-patent-data',
    'Name': 'finland-ransom/Egentliga Finland_11_16_1_255_gray_dither.jpeg'
  }
  },
  FeatureTypes=["TABLES", "FORMS"]
  
})

print(response)
```


```{python}

file = "data/riksvakanslistan/top-left-table.PNG"
from pyprojroot import here

here("data/riksvakanslistan/top-left-table.PNG")

textract_python_table_parser.py here("data/riksvakanslistan/top-left-table.PNG")

```


```{r}
image <- image_read(here("data", "riksvakanslistan", "kontor.PNG"))

image %>% 
  # have to tune this parameter
  image_deskew(threshold = 1000) %>% 
  image_despeckle() %>% 
  image_quantize(max = 255, colorspace = "gray", dither = T) %>% image_write(here("data", "riksvakanslistan", "kontor_processed.PNG"))

image <- image_read(here("data", "riksvakanslistan", "kontor_processed.PNG"))

text <- image %>% 
  image_ocr(language = "swe")


text %>% 
  as_tibble() %>% 
  separate_rows(value, sep = "\\;") %>% 
  mutate(value = str_remove(value, "Kontor i:"),
         value = str_squish(value)) %>% 
  separate(value, into = c("Region", "Offices"), sep = "\\:") %>% 
  mutate(Offices = str_squish(Offices))

cities <- text %>% 
  as_tibble() %>% 
  separate_rows(value, sep = "\\;") %>% 
  mutate(value = str_remove(value, "Kontor i:"),
         value = str_squish(value)) %>% 
  separate_rows(value, sep = "\\:|\\,") %>% 
  mutate(value = str_squish(value))
```

Geocoding

```{r}
library(tidygeocoder)


  

census_s1 <- cities %>% 
  mutate(city = str_c(value, ", Sweden")) %>%
  geocode(address = city, verbose = TRUE)

# census_s1 %>% write_rds("data/riksvakanslistan/office_locations.rds")

library(sf)

census_s1 %>% 
  ggplot(aes(long, lat, label = city)) +
  geom_point() +
  coord_sf() +
  borders(regions = "Sweden")
```


```{r}
c("Södertälje",
  "Norrtälje",
  "Enköping",
  "Tierp",
  "Skutskärp",
  "Nyköping",
  "Strängnäs",
  "Katrineholm",
  "Gnesta",
  "Flen",
  "")
```





```{r}
image <- image_read(here("data", "riksvakanslistan", "IMG_8073_crop.jpg"))

image %>% 
  # have to tune this parameter
  image_deskew(threshold = 1000) %>% 
  image_despeckle() %>% 
  image_quantize(max = 255, colorspace = "gray", dither = T) %>% 
  image_rotate(.5) %>% 
  image_write(here("data", "riksvakanslistan", "IMG_8073_crop_processed_1.jpg"))

image <- image_read(here("data", "riksvakanslistan", "IMG_8073_crop_processed_1.jpg"))

text <- image %>% 
  image_ocr(language = "swe")


text %>% 
  as_tibble() %>% 
  separate_rows(value, sep = "\\;") %>% 
  mutate(value = str_remove(value, "Kontor i:"),
         value = str_squish(value)) %>% 
  separate(value, into = c("Region", "Offices"), sep = "\\:") %>% 
  mutate(Offices = str_squish(Offices))

cities <- text %>% 
  as_tibble() %>% 
  separate_rows(value, sep = "\\;") %>% 
  mutate(value = str_remove(value, "Kontor i:"),
         value = str_squish(value)) %>% 
  separate_rows(value, sep = "\\:|\\,") %>% 
  mutate(value = str_squish(value))
```

