---
title: "Google Patents Scraper"
author: "JJayes"
date: "20/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

Scraping google patents for information about electricity related patents in Sweden.

# Process

Has three parts:

1. List of pages to scrape

2. Scraper script

3. Iterator

## List of pages to scrape

```{r}
library(dplyr)
library(readr)
library(stringr)
library(tidyr)
library(purrr)

# or
library(tidyverse)
library(rvest)
library(here)

```

```{r}
df <- read_rds(here("data", "patent-info-google", "Electricity_patents_list_Google_Patents.rds"))

list_of_pages <- df %>% 
  select(id, patent_url = result_link)
```

## Scraper Script

Things I want from the patent page:

* Title
* Description and claims text
* Countries where patent is registered
* Other citations
* Forward links to other patents
* Patents that this patent cites
* Also published as
* Similar documents
* Concepts that are mentioned in the patent

```{r}
get_patent_info <- function(patent_url) {
  
  Sys.sleep(.5)
  
  # message so we know it's doing something
  message(paste0("Getting patent info from ", patent_url))
  
  # get html
  html <- read_html(patent_url)
  
# title
  title <- html %>%
    html_nodes("title") %>%
    html_text(trim = T) %>%
    str_squish() %>%
    str_remove(., " - Google Patents")
  
# abstract
  abstract <- html %>% 
    html_nodes(".abstract") %>% 
    html_text(trim = T)
  
# text
  description_text <- html %>%
    html_nodes(".description-paragraph") %>%
    # html_nodes(".notranslate") %>%
    # html_nodes("span") %>%
    html_text(trim = T) %>%
    as_tibble() %>%
    nest(desc_text = c(value))

  claims_text <- html %>%
    html_nodes(".claim-text") %>%
    html_text(trim = T) %>%
    as_tibble() %>%
    nest(claim_text = c(value))
  
# countries
  countries <- html %>%
    html_nodes("[itemprop='countryStatus']") %>%
    html_nodes("[itemprop='countryCode']") %>%
    html_text() %>% paste0(collapse = ", ")
  
# forwardReferences
# url
forwardReferences_links <- html %>%
  html_nodes("[itemprop='forwardReferences']") %>%
  html_nodes("a") %>%
  html_attr("href") %>%
  as_tibble() %>%
  nest(forwardReferences_link = c(value))

# publicationNumber
forwardReferences_p_numbers <- html %>%
  html_nodes("[itemprop='forwardReferences']") %>%
  html_nodes("[itemprop='publicationNumber']") %>% 
  html_text() %>%
  as_tibble() %>% 
  nest(forwardReferences_p_number = c(value))

# primaryLanguage
forwardReferences_p_langs <- html %>%
  html_nodes("[itemprop='forwardReferences']") %>%
  html_nodes("[itemprop='primaryLanguage']") %>% 
  html_text() %>%
  as_tibble() %>% 
  nest(forwardReferences_p_lang = c(value))

# publicationDate
forwardReferences_p_dates <- html %>%
  html_nodes("[itemprop='forwardReferences']") %>%
  html_nodes("[itemprop='publicationDate']") %>% 
  html_text() %>% 
  lubridate::ymd() %>% 
  as_tibble() %>% 
  nest(forwardReferences_p_dates = c(value))

# assigneeOriginal
forwardReferences_assigneeOriginals <- html %>%
  html_nodes("[itemprop='forwardReferences']") %>%
  html_nodes("[itemprop='assigneeOriginal']") %>% 
  html_text() %>% 
  as_tibble() %>% 
  nest(forwardReferences_assigneeOriginal = c(value))

# stopping with backward refs for now

# concepts
  ids <- html %>%
    html_nodes("[itemprop='concept']") %>%
    html_nodes("[itemprop='id']") %>%
    html_text()

  names <- html %>%
    html_nodes("[itemprop='concept']") %>%
    html_nodes("[itemprop='name']") %>%
    html_text()

  counts <- html %>%
    html_nodes("[itemprop='concept']") %>%
    html_nodes("[itemprop='count']") %>%
    html_text()

  concepts <- tibble(ids, names, counts) %>%
    nest(concepts = c(ids, names, counts))
  
  output <- tibble(
    title,
    abstract,
    description_text,
    concepts,
    claims_text,
    countries,
    forwardReferences_links,
    forwardReferences_p_numbers,
    forwardReferences_p_langs,
    forwardReferences_p_dates,
    forwardReferences_assigneeOriginals
  )
  
  output
}

```

Works aight!

```{r}
list_of_pages %>% 
  slice_sample(n = 5) %>% 
  head(1) %>% 
  select(patent_url) %>% 
  pull()

test <- get_patent_info("https://patents.google.com/patent/SE432859B/en")

test %>%
  unnest(concepts)
```

## Iterator

```{r}
test <- list_of_pages %>% 
  slice_sample(n = 5) %>% 
  head(1) %>% 
  mutate(patent_info = map(patent_url, get_patent_info))
```

```{r}
test %>% unnest(patent_info) %>% view
```





Reworking

```{r}
html %>% 
  html_nodes("h2")

html %>% 
  html_nodes("table") %>% 
  html_table()


tables <- html %>% 
  html_table()

tables_1 <- map_dfr(tables[-1], ~ nest(.)) %>% 
  mutate(table = row_number()) 

tables_1 %>% 
  head(1) %>% 
  unnest(data) %>% 
  pivot_longer(c(everything(), - table), names_to = "names", values_to = "value") %>% 
  mutate(value = str_squish(value))

do_to_tbl <- function(tbl) {
  tbl %>% 
    pivot_longer(c(everything()), names_to = "names", values_to = "value") %>%
    mutate(value = str_squish(value)) %>% 
    nest(contents = everything())
}

test <- tables_1 %>%
  mutate(test = map_df(data, do_to_tbl))

test %>% unnest(test) %>% 
  unnest(contents) %>%
  filter(table == 6) %>% 
  pivot_wider(names_from = names, values_from = value) %>% 
  janitor::clean_names()
```

