---
title: "Untitled"
author: "JJayes"
date: "02/02/2022"
output: html_document
---

### Scraping info from SCB's website.



```{r}
library(tidyverse)

df <- readxl::read_excel("data/SCB-occupations/ssyk_index_webb_2022.xlsx")

df <- df %>% 
  janitor::clean_names() %>% 
  mutate(ssyk_2012_kod = as.character(ssyk_2012_kod),
         ssyk_2012_kod  = ifelse(nchar(ssyk_2012_kod) == 3, str_c("0", ssyk_2012_kod ), ssyk_2012_kod ))
```

How many specific occupations?

```{r}
codes <- df %>% 
  distinct(ssyk_2012_kod)
```

430

```{r}
codes <- codes %>% 
  mutate(url = str_c("https://www.h5.scb.se/yreg/SSYKBeskr2012.asp?id=", ssyk_2012_kod))
```


### Function to get info

```{r}
library(rvest)

get_occupation_info <- function(url) {
  message(paste0("Getting info about code: ", url))
  Sys.sleep(.5)
  html <- read_html(url)

  table <- html %>%
    html_table()

  table <- table[[1]]

  table %>%
    pivot_longer(everything()) %>%
    distinct(value) %>%
    mutate(cols = c("code", "title", "description")) %>%
    pivot_wider(names_from = cols)
}
```


```{r}
# codes_desc <- codes %>% 
#   # head() %>% 
#   mutate(info = map(url, possibly(get_occupation_info, "failed")))
# 
# codes_desc_1 <- codes_desc %>% 
#   filter(info != "failed") %>% 
#   unnest(info) 
# 
# codes_desc_2 <- codes_desc %>% 
#   filter(info == "failed") %>% 
#   mutate(info = map(url, possibly(get_occupation_info, "failed")))
# 
# codes_desc_2 %>%
#   filter(info != "failed") %>% 
#   unnest(info) %>% 
#   bind_rows(codes_desc_1) %>%
#   write_rds("data/SCB-occupations/ssyk_descriptions.rds")
```


### Translate!

```{r}
df <- read_rds("data/SCB-occupations/ssyk_descriptions.rds")

df %>% mutate(nchar = nchar(description)) %>% 
  ggplot(aes(nchar)) +
  geom_histogram()
```

### Put csv on Github

```{r}
# df %>% write.csv("data/SCB-occupations/ssyk_descriptions.csv")
```

Used Mbart50 to translate on a Google Colab workbook.

```{r}
# read in translations and combine.
df <- read.csv("data/SCB-occupations/df_translated.csv")
```


```{r}
df <- df %>% 
  as_tibble() %>% 
  mutate(ssyk_2012_kod = as.character(ssyk_2012_kod),
         ssyk_2012_kod  = ifelse(nchar(ssyk_2012_kod) == 3, str_c("0", ssyk_2012_kod ), ssyk_2012_kod )) %>% 
  select(ssyk_2012_kod, english)

df_orig <- read_rds("data/SCB-occupations/ssyk_descriptions.rds")

df <- df_orig %>% 
  inner_join(df, by = "ssyk_2012_kod")

df <- df %>% 
  mutate(english = str_remove(english, "\\['"),
         english = str_remove(english, "'\\]"),
         english = str_remove(english, '\\["'),
         english = str_remove(english, '"\\]'))

df <- df %>% 
  mutate(occ_group = str_extract(code, "[0-9]")) %>% 
  mutate(occ_group_name = str_replace_all(occ_group, 
                                          c("0" = "Amed forces",
                                            "1" = "Managers",
                                            "2" = "Professionals",
                                            "3" = "Technicians",
                                            "4" = "Clerks",
                                            "5" = "Service and sales",
                                            "6" = "Agric, forest and fisheries",
                                            "7" = "Craft and related trades",
                                            "8" = "Machine operators",
                                            "9" = "Elementary occupations")))

# df %>% write_rds("data/SCB-occupations/df_translated_joined.rds")
```

Explore words

```{r}
library(tidytext)

df <- read_rds("data/SCB-occupations/df_translated_joined.rds")

df %>% 
  unnest_tokens(word, english) %>% 
  anti_join(stop_words) %>% 
  count(word, sort = T)

```


## Modelling

I want to do UMAP based on TF-IDF in the english descriptions - will colour the dots based on code and plot them on a UMAP 2d space.

```{r}
df_mod <- df %>% 
  select(code, english, occ_group_name)

library(recipes)
library(textrecipes)
# library(embed)

pca_rec <- recipe(code ~ ., data = df_mod) %>% 
  update_role(code, occ_group_name, new_role = "id") %>% 
  step_tokenize(english) %>% 
  step_stopwords(english) %>%
  step_tokenfilter(english, max_tokens = 30) %>% 
  step_tfidf(english) %>% 
  step_pca(all_numeric_predictors(), keep_original_cols = T)

pca_juiced <- pca_rec %>% prep() %>% juice()

pca_juiced %>% 
  ggplot(aes(PC1, PC2, colour = occ_group_name)) +
  geom_point() +
  labs(colour = "Occupational group")
```

What can we say about the different components?

```{r}
pca_prep <- prep(pca_rec)

pca_comps <- tidy(pca_prep, 5) %>% 
  filter(component %in% paste0("PC", 1:4)) %>% 
  group_by(component) %>% 
  top_n(8, abs(value)) %>% 
  ungroup()


pca_comps %>% 
  mutate(terms = str_remove(terms, "tfidf_english_"),
         sign = value > 0,
         value = abs(value),
         terms = fct_reorder(terms, value)) %>% 
  ggplot(aes(value, terms, fill = sign)) +
  geom_col() +
  facet_wrap(~ component, scales = "free")
```



Do with UMAP

```{r}
umap_rec <- recipe(code ~ ., data = df_mod) %>% 
  update_role(code, occ_group_name, new_role = "id") %>% 
  step_tokenize(english) %>% 
  step_stopwords(english) %>% 
  step_tokenfilter(english, max_tokens = 100) %>% 
  step_tfidf(english) %>% 
  step_umap(all_numeric_predictors())

umap_juiced <- umap_rec %>% prep() %>% juice()

umap_juiced %>% 
  ggplot(aes(UMAP1, UMAP2, colour = occ_group_name)) +
  geom_point() +
  labs(colour = "Occupational group")
```

## What is most specific about each occupational class


```{r}
library(tidylo)

tidy_bigrams <- df %>% 
  unnest_tokens(bigram, english, token = "ngrams", n = 1, to_lower = T) %>% 
  anti_join(stop_words, by = c("bigram" = "word"))

bigram_counts <- tidy_bigrams %>% 
  count(occ_group_name, bigram, sort = T)

bigram_log_odds <- bigram_counts %>% 
  bind_log_odds(occ_group_name, bigram, n)

bigram_log_odds %>% 
  filter(n > 5) %>% 
  arrange(-log_odds_weighted)
```

```{r}

jpeg(filename = "figures/SCB-occupations/log_odds_SCB.jpeg",
     height = 8,
     width = 12,
     units = "in",
     res = 1000)

bigram_log_odds %>%
  group_by(occ_group_name) %>%
  slice_max(log_odds_weighted, n = 10, with_ties = F) %>%
  ungroup() %>%
  mutate(bigram = reorder_within(bigram, log_odds_weighted, occ_group_name)) %>%
  ggplot(aes(log_odds_weighted, bigram, fill = occ_group_name)) +
  geom_col(show.legend = FALSE) +
  scale_y_reordered() +
  facet_wrap(~occ_group_name, scales = "free") +
  labs(x = NULL,
       y = NULL,
       # title = "Words that are most specific to each occupational group"
       ) 

dev.off()
```


```{r}


```
